Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits

### 2015-12-08 ms.tex
begin rewrite

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$). The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2014} of richness \citeeg{Abell1958,Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.

@@

\subsection{Mock Observations}\label{sec:observations}
\editorial{Not sure this does a good enough job talking about the two different observations.}
Tentatively slated to start in the fall of 2015, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, Spring field and 120 \degsq, Fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

@@

\section{Cluster Membership}
In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known. In reality, galaxy over densities will be detected from imaging surveys \citeeg{Rykoff2014} or through techniques to identify structure in the RA, DEC, z point data (\eg, DBSCAN; \citealt{Ester1996}).

While the galaxy cluster center may be well known, the constituent galaxies will not. The identification of member galaxies from photometric data \citeeg{Rozo2014} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space. \editorial{Not very happy about that sentence}.

We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information. After an initial cut of $cz_c \pm 10,000$ \kms, the galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 (arbitrarily chosen) galaxies. Galaxies farther than 3 Mpc from the cluster center are also rejected. Once binned, the galaxies are sorted by their line-of-sight velocity (LOSV; see Section~\ref{sec:LOSVD}). Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.

\editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework. I think what we'll do is center a 100'' box on all of the clusters and then try to recover the galaxies. How many will we get, how many are wrong, and can we do better with a different algorithm?}

@@

\subsection{Radial Extent}
We define the radius of a galaxy cluster as
\begin{equation}
	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
\end{equation}
where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.

\section{RESULTS}\label{sec:results}
The results of this work come in two broad sections. The accuracy of which we determine each cluster's LOSVD and dynamical mass, and the probability given a determined mass it is the correct mass. We test two different observation strategies with ideal and realistic information about the membership of the observed galaxies. Ideal information is knowing the exact membership of the galaxies, and realistic information relies on methods to determine the membership. \editorial{The results of this section a shown in Figures XXX and Figures XXX for the LOSVD and masses respectively.}

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
	\caption{Intrinsic cluster properties versus the recovered cluster properties for 16758 unique halos comprised of 657916 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:full} 
\end{figure*}

\begin{figure*} 
	\includegraphics[width=\textwidth]{hetdexDepth.pdf} 
	\caption{HETDEX DEPTH! Intrinsic cluster properties versus the recovered cluster properties for 14239 unique halos comprised of 87754 individual galaxies. The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass. In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.} 
	\label{fig:hetdexDepth} 
\end{figure*}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$). The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2015} of richness \citeeg{Abell1958, Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.

@@

\subsection{Mock Observations}\label{sec:observations}
\editorial{Not sure this does a good enough job talking about the two different observations.}
Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

@@

% \section{Cluster Membership}
% In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known. In reality, galaxy over densities will be detected from imaging surveys \citeeg{Rykoff2014} or through techniques to identify structure in the RA, DEC, z point data (\eg, DBSCAN; \citealt{Ester1996}).
%
% While the galaxy cluster center may be well known, the constituent galaxies will not. The identification of member galaxies from photometric data \citeeg{Rozo2015} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space. \editorial{Not very happy about that sentence}.
%
% We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information. After an initial cut of $cz_c \pm 10,000$ \kms, the galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 (arbitrarily chosen) galaxies. Galaxies farther than 3 Mpc from the cluster center are also rejected. Once binned, the galaxies are sorted by their line-of-sight velocity (LOSV; see Section~\ref{sec:LOSVD}). Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.
%
% \editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework. I think what we'll do is center a 100'' box on all of the clusters and then try to recover the galaxies. How many will we get, how many are wrong, and can we do better with a different algorithm?}

@@

% \subsection{Radial Extent}
% We define the radius of a galaxy cluster as
% \begin{equation}
% 	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
% \end{equation}
% where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.

\section{RESULTS}\label{sec:results}

\subsection{Recovery of Clusters}
\begin{figure*} 
	\includegraphics[width=\textwidth]{recovery.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:recovery} 
\end{figure*}

The results of this work come in two broad sections. The accuracy of which we determine each cluster's LOSVD and dynamical mass, and the probability given a determined mass it is the correct mass. We test two different observation strategies with ideal and realistic information about the membership of the observed galaxies. Ideal information is knowing the exact membership of the galaxies, and realistic information relies on methods to determine the membership. \editorial{The results of this section a shown in Figures XXX and Figures XXX for the LOSVD and masses respectively.}

@@

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
